Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-10-29 paper/main.tex
add keywords for title
extend general comment
add image for mie potential

% keywords can be removed
% \keywords{}

@@

\textbf{
    Was mir hier nicht gefällt, ist, dass du von Parameter schätzen bei ABMs kommend ziemlich
    detailliert über Mechanik redest.
    Das passt nicht.
    Man erwartet mehr Infos über den Blueprint und ist verwirrt.
    Worum geht es hier?
}
\textit{Ich habe den blueprint vollkommen entfernt. Er macht kein Sinn im MS.}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{docs/source/_static/mechanics.png}
    \caption{
        Example of an elonged bacterial rod represented by a collection of vertices which are
        connected by springs.
        The angles $\alpha_i$ will be used to model the rigidity of the rod.
        A bacterial agent which is not interacting with any external objects will tend to the
        equilibrium state of a straight rod with no curvature.
    }
    \label{fig:mechanics-bacterium}
\end{figure}

>>>>

\textbf{Discussed Keywords (Working Title)}
\begin{itemize}
    \item Parameter Estimation
    \begin{itemize}
        \item Mechanical Properties
        \item Rod-shaped?
        \item Single-cell
    \end{itemize}
    \item \ac{abm}
    \item Methods
\end{itemize}
% keywords can be removed
% \keywords{}

@@

\textbf{
    Was mir hier nicht gefällt, ist, dass du von Parameter schätzen bei ABMs kommend ziemlich
    detailliert über Mechanik redest.
    Das passt nicht.
    Man erwartet mehr Infos über den Blueprint und ist verwirrt.
    Worum geht es hier?
}
\textit{Ich habe den blueprint vollkommen entfernt. Er macht kein Sinn im MS. Der Rest sollte noch
angepasst werden.}

@@

\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.5\textwidth]
        {docs/source/_static/mechanics.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.5\textwidth]
        {docs/source/_static/mie-potential-shapes.pdf}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}%
    \caption{
        (A) Example of an elonged bacterial rod represented by a collection of vertices which are
        connected by springs.
        The angles $\alpha_i$ will be used to model the rigidity of the rod.
        A bacterial agent which is not interacting with any external objects will tend to the
        equilibrium state of a straight rod with no curvature.
        (B) Potential curves of the Mie potential for various combinations of exponents $n,m$ with
        upper bound $\beta=2.5U_0$ and cutoff $\zeta=3(R_1+R_2)$.
        \textbf{TODO insert more (possibly schematic depictions of how the model works
        (Interactions, Cycle))}
    }
    \label{fig:model-bacterium}
\end{figure}
